Dear Hiring Manager,
I am excited to submit my application for the Early Career Program in ASML.
As a recent graduate from the Faculty of Physics in Rijeka, I have gained a solid foundation in theoretical and experimental physics,
with a specific focus on solid-state physics, semiconductors, as well as optics.
Throughout my journey I've had an interest in lithography and the semiconductor industry, and an unyielding interest for physics and computers!
This, along with my experience working with lasers in the quantum and non-linear optics laboratory in Rijeka
has helped me develop strong design, data analysis, and critical thinking skills, which I believe will be invaluable in contributing to the ASML team.
I am drawn to the Early Career Program because of the company's commitment to innovation and cutting-edge technology, as well as my own personal betterment. 
I am confident that my capability to improve, combined with my strong analytical and problem-solving skills, make me an good candidate for this program. 
I am highly motivated to learn from and collaborate with experienced professionals in the field, and I believe that this program will provide me with the necessary resources to grow and excel in my career.\\

If, by some chance you are reading this letter, thank you for considering my application. I look forward to the opportunity to contribute to the ASML team and to learn from the best in the industry.
Please do not hesitate to contact me if you have any further questions or if you require any additional information.
